---
title: "Data Science Application"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    theme: flatly

#YAML configuration
---

```{r}
library(dplyr)
library(ggplot2)
library(plotly)
library(tree)
```

Sidebar {.sidebar}
===

```{r}
fileInput(inputId = "metadata",label = "Please Upload a CSV File")
```

Summary
===


Row
---

###Preview of the File

```{r}
tableOutput("data_preview")
```


```{r}
observe({
  if(is.null(input$metadata))
    return(NULL)
  data = read.csv(input$metadata$datapath)
  output$data_preview = renderTable(head(data))
  
  checknum = sapply(data,is.numeric)
  numcol = names(data)[checknum]
  catcol = names(data)[!checknum]
  
  output$colnames = renderTable(names(data))
  output$numericcols = renderTable(numcol)
  output$categcols = renderTable(catcol)
  
  output$dropdown = renderUI(selectInput(inputId = "select_column",label = "Select a column",choices = names(data)))
  output$ddnumeric = renderUI({selectInput(inputId = "select_numeric",label = "Select a column", choices = numcol,multiple = TRUE,selected = numcol[1])})
  output$ddcateg = renderUI({selectInput(inputId = "select_categ",label = "Select a column", choices = catcol)})
  
  output$boxplot = renderPlot({boxplot(data[,input$select_numeric])})
  
  output$hist = renderPlot({hist(data[,input$select_numeric])})
  
  output$freq_category = renderPlot({
    items_freq = data %>% group_by_(input$select_categ) %>% summarise(count_item=n()) %>% arrange(-count_item) %>% head(5)
    ggplot(items_freq,aes_string(x=input$select_categ,y="count_item"))+geom_bar(stat="identity")
  })
  
  output$scatterplot = renderPlot({
     plot(data[,input$select_numeric])
   })
  
  output$cluster_table=renderTable({
   data_num=data[,numcol]
   fit=kmeans(na.omit(data_num), centers = input$n_cluster)
   table(fit$cluster)
 })
 
 output$cluster_slider=renderUI({
   sliderInput(inputId = "n_cluster",label="choose number of clusters",min=1,max=15,value=5)
 })
  
 output$dec_input = renderUI({
   selectInput(inputId = "dep_var",label = "Select input variable",choices = names(data))
 })
 
 output$dec_target = renderUI({
   selectInput(inputId = "indep_var",label = "Select output variable",choices = names(data),multiple = TRUE)
 })
 
  output$dtree = renderPlot({
       target = input$dep_var
       inputs = paste (input$indep_var, collapse = '+')
       fit_eqn = paste(target ,'~', inputs)
       dtree = tree(fit_eqn,data)
       plot(dtree)
       text(dtree)
     })  
  
})
  
  

  
```

Row
---

###Column Names
```{r}
tableOutput("colnames")
```

###Numerical Columns
```{r}
tableOutput("numericcols")
```

###Categorical Columns
```{r}
tableOutput("categcols")
```

Numerical Columns
===

Row {data-height=300}
---

###Dropdowns
```{r}
uiOutput("ddnumeric")
```

###Scatterplot
```{r}
plotOutput("scatterplot")
```

Row
---

###Histogram

```{r}
plotOutput("hist")
```

###Boxplot
```{r}
plotOutput("boxplot")
```




Categorical Columns
===

Row {data-height = 300}
---

###Dropdowns
```{r}
uiOutput("ddcateg")
```

Row
---

###Frequency Distribution

```{r}
plotOutput("freq_category")
```

K-Nearest Neighbours
===

Row
---
###Selecting number of centres
```{r}
uiOutput("cluster_slider")
```

###Cluster Table
```{r}
tableOutput("cluster_table")
```

Decision Tree
===

Row
---
###Prediction Label
```{r}
uiOutput("dec_input")
```

###Predictors
```{r}
uiOutput("dec_target")
```


Row
---

###Plot
```{r}
plotOutput("dtree")
```


fit = tree(fit_equ,data= data)
plot(fit)
text(fit)
